%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Abhijeet Singh Panwar} \\ \vspace{1pt}
    \small +91 9352471582 $|$ \href{mailto:x@x.com}{\underline{iabzeet@gmail.com}} $|$ 
    \href{https://linkedin.com/in/...}{\underline{linkedin.com/in/abhijeet-singh-panwar}} $|$
    \href{https://github.com/...}{\underline{github.com/iabzeet}}
\end{center}

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Kotlin, Dart, JavaScript, Python, C/C++, (DSA in Java)} \\
     \textbf{Mobile Development}{: Android (Java/Kotlin), Jetpack Compose, Jetpack Components (Room, LiveData, ViewModel)} \\
     \textbf{Flutter Development}{: State Management (Provider, Riverpod, BLoC), Material-UI} \\
     \textbf{UI/UX Design}{: Jetpack Compose, XML, Material Design} \\
     \textbf{Web Technologies}{: RESTFul APIs, Bootstrap, JSON, FastAPI} \\
     \textbf{Cloud Technologies}{: Firebase (Authentication, Firestore, Cloud Functions, Cloud Messaging), AWS, Google Cloud Plaform} \\
     \textbf{Databases}{: Room Database, SQLite, Firebase Realtime Database, Firestore, Hive, ISAR, MySQL, MongoDB} \\
     \textbf{Frameworks}{: Android, Flutter, Jetpack Compose, React, Node.js, Flask} \\
     \textbf{Developer Tools}{: Android Studio, Git, CI/CD, Linux (Arch, Kali), Virtual Box} \\
     \textbf{Libraries}{: pandas, NumPy, Matplotlib (for data analysis and visualization)} \\
    \textbf{Testing}{: Unit Tests, Widget Tests, Integration Tests, Flutter Testing Framework} \\
    }}
 \end{itemize}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Arya College of Engineering}{Jaipur, Raj.}
      {Bachelor of Technology}{2021 -- 2025}
    \resumeSubheading
      {Gurudeep Academy}{Beawar, Raj.}
      {(RBSE) Class 12$^{\text{th}}$}{2019}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Global Institute}{July 2023 -- Sept 2023}
      {Web Development Training}{}
      \resumeItemListStart
        \resumeItem{Developed 10+ responsive and interactive websites using HTML, CSS, Bootstrap and JavaScript; optimized load times by 40\% and increased user engagement metrics by 25\%.}
        \resumeItem{Engineered a high performing e-commerce platform using Django, integrating robust features: user authentication, expansive product catalog, seamless shopping cart functionality, and secure payment gateaways.}
        \resumeItem{Explored ways to visualize GitHub collaboration in a classroom setting}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{The Wall} $|$ \emph{Flutter, Dart, Provider, Firebase (Authentication, Firestore, Cloud Functions), Material Design}}{}
          \resumeItemListStart
            \resumeItem{The Wall is a social media application developed using Flutter, designed to provide users with a seamless and interactive platform similar to Twitter. This app allows users to post messages on a common wall, reply to messages, and like posts. The app supports user customization, including setting a username and bio. It also adapts to the user's mobile theme, offering a dark mode that aligns with the device settings.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Food Delivery} $|$ \emph{Flutter, Dart, Provider, Firebase (Authentication, Firestore), Razerpay API, Location API}}{}
          \resumeItemListStart
            \resumeItem{FoodieDeliver is a mobile application designed to simplify the process of ordering food online. Built using Flutter, the app leverages location APIs to determine the user's location, providing a personalized experience. The home screen features sections of different types of foods displayed in a horizontally scrollable view, enhancing user accessibility and navigation through food categories.}
            \resumeItem{FoodieDeliver provides estimated delivery times for orders and a comprehensive cart management system where users can review selected items, adjust quantities, and add optional add-ons tailored to each food item.}
            \resumeItem{The billing page features a structured layout that summarizes the order details, ensuring clarity and transparency in transaction summaries.}
          \resumeItemListEnd
     \resumeProjectHeading
          {\textbf{My Maps} $|$ \emph{Kotlin, Google Maps API, Room Database, ViewModel}}{}
          \resumeItemListStart
            \resumeItem{The Custom Maps app is a location-based Android application developed using Kotlin, designed to enable users to create and manage custom maps with personalized pins and descriptions.}
            \resumeItem{Upon opening the app, users are greeted with an intuitive interface featuring an action floating button. Clicking this button prompts the user to enter a title for their map. Once the title is provided, the app utilizes the Google Maps API to display the user's current location on the map.}
            \resumeItem{User can long tap on the map and save the location wile giving it the custom title and description. The user can also delete these pins.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%


%-------------------------------------------
\end{document}
